---
output:
  html_document:
    self_contained: no
---
Reproducible Research - Peer Assessment 1
=========================================

## Load and Pre-process data


- Download as zip
- unzip to csv
- Preprosses the data

```{r load_data, echo=TRUE}


zip_url <- "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
temp <- tempfile()
download.file(zip_url, temp, mode="wb")
unzip(temp,"activity.csv")
data <- read.table("activity.csv", sep=",", header=TRUE)
unlink(temp)

library(dplyr)
data_by_date <- group_by(data, date)
```

## Steps in a day

1. Calculate the total number of steps in a day
2. Plot a histogram of total number of steps in a day
3. Calculate mean and median of total number of steps in a day

```{r num_steps_per_day, echo=TRUE}

steps_by_date <- summarise(data_by_date, steps=sum(steps))

hist(steps_by_date$steps,
     main="Steps per day",
     xlab="Number of steps in a day")

final_steps_by_date <- summarise(steps_by_date,
                                 avg_steps=mean(steps,na.rm=TRUE),
                                 med_steps=median(steps,na.rm=TRUE))

avgstp <- final_steps_by_date[1,1]
medstp <- final_steps_by_date[1,2]
```
The average number of steps in a day is `r avgstp`  
The median number of steps in a day is `r medstp`

## Average daily activity pattern
1.  Time series  plot of 5-minute intervals and average number of steps taken
2.  Which 5-minute interval contains the maximum number of steps

```{r daily-activity_patter, echo=TRUE}

data_by_interval <- group_by(data, interval)

steps_by_interval <- summarise(data_by_interval, steps=mean(steps, na.rm=TRUE))

library(ggplot2)
qplot(interval, steps, data=steps_by_interval, type="1",
      main="Average daily activity pattern",
        xlab="5 minute interval",
        ylab="Average number of steps")

max_steps <- max(steps_by_interval$steps)
max_steps_interval <- subset(steps_by_interval, steps==max_steps)

msi <- max_steps_interval[1,1]
mss <- max_steps_interval[1,2]

```

The interval which, on average across all days in the dataset, that contains the maximum number of steps is `r msi`  
This interval has `r mss` steps on average

## Inputing missing values

``` {r num_missing_vals, echo=TRUE}
num_na <- sum(is.na(data$steps))

```

### Strategy

There are `r num_na` missing values in the data set

My feeling is that people would be very consistent in their behaviour over a week.  That is, they would do the same thing at the same time.  For example, leave for work at 7:30am of a weekday, go for a walk/jog at 6am on Mon, Wed, and Fri.  Therefore, I would replace missing values with the mean value the 5-minute interval.  That is, the number of steps for 8:00am, would be replaced with the mean number of steps for 8:00am across the data set.


``` {r replace_missing-vals, echo=TRUE}
all_data <- cbind(data_by_date, steps_by_interval)
colnames(all_data) <- c("steps", "date", "interval", "mean_interval", "mean_steps")
all_data$steps <- replace(all_data$steps, is.na(all_data$steps), all_data$mean_steps)

sbdnn_by_date <- group_by(all_data, date)
steps_by_date_no_na <- summarise(sbdnn_by_date, steps=sum(steps))

hist(steps_by_date_no_na$steps,
     main="Steps per day - NA replaced by mean",
     xlab="Number of steps in a day")

final_steps_by_date_no_na <- summarise(steps_by_date_no_na,
                                 avg_steps=mean(steps),
                                 med_steps=median(steps))

avgstp_no_na <- final_steps_by_date_no_na[1,1]
medstp_no_na <- final_steps_by_date_no_na[1,2]
```
The average number of steps in a day is `r avgstp_no_na`  
The median number of steps in a day is `r medstp_no_na`



## Differences between weekdays
Unfortunately, due to personal reasons, I was unable to complete this task
